# surveybuilder: Make Surveys and Randomized Survey Experiments in R

`surveybuilder` is a package for creating surveys in PDF format using R, 
and can accomodate a range of in-built and custom randomization schemes. 
It also makes the generation and numbering of survey modules and questions
much easier and quicker than manual PDF methods. 
`surveybuilder` compiles surveys in the $\LaTeX$ environmet, using the 
`paperandpencil` package, 
designed by Miriam Dieter & Anja Zwingenberger at 
University of Duisburg-Essen in 2009, 
[see here for more details](http://www.qdds.org/).

You can install `surveybuilder` using the following code:

```{r,eval=F}
library(devtools)
install_github(repo = "surveybuilder",
               username = "jaspercooper")
```

Load as follows:

```{r,eval=T}
library(surveybuilder)
```

# Making questions 

## Open questions 

All questions have an optional question prompt and comment option. 
Open questions can be followed by an arbitrary number of lines or dots. 

```{r}
# No lines, no comment
make_open_question(
  question_prompt = "How was your day?",
  concat = T)
# With comment
make_open_question(
  question_prompt = "How was your day?",
  comment = "\\emph{I honestly want to know!}",
  concat = T)
# With 1 line
make_open_question(
  question_prompt = "How was your day?",
  comment = "\\emph{I honestly want to know!}",
  N_lines = 1,
  concat = T)
# With 2 dotted lines
make_open_question(
  question_prompt = "How was your day?",
  comment = "\\emph{I honestly want to know!}",
  N_dot_lines = 2,
  concat = T)
```

## Multiple choice questions 

Multiple choice questions can be formatted in horizontal or vertical styles.

```{r}
# Horizontal with labels on top
make_horizontal_question(
  question_prompt = "How likely are you to use this package?",
  upper_labels = c("Not a chance",
                   "Maybe once in a while",
                   "Literally. Every. Day."),  
  concat = T)
# Horizontal with labels on bottom
make_horizontal_question(
  question_prompt = "How likely are you to use this package?",
  lower_labels = c("Not a chance",
                   "Maybe once in a while",
                   "Literally. Every. Day."),
  concat = T)
# Horizontal with labels on top and bottom
make_horizontal_question(
  question_prompt = "How likely are you to use this package?",
  upper_labels = c("Not a chance",
                   "Maybe once in a while",
                   "Literally. Every. Day."),
  lower_labels = c(1,2,3),
  concat = T)
# Vertical
make_vertical_question(
  question_prompt = "How likely are you to use this package?",
  labels = c("Not a chance",
             "Maybe once in a while",
             "Literally. Every. Day."),
  concat = T)
```

## Numeric questions

You can add questios with number boxes for measurement (years, meters, events, etc.).

```{r}
# For a single box
make_numeric_question(
  question_prompt = "How many hours have you spent writing surveys in Excel and Word?",
  labels = c("minutes","hours","days"),
  N_boxes = c(2,2,1),
  concat = T)
# For five boxes, with different labels at different points
make_numeric_question(
  question_prompt = "How many hours have you spent writing surveys in Excel and Word?",
  labels = c("minutes","hours","days"),
  N_boxes = c(2,2,1),
  concat = T)
```

Note that `cm_from_left` can be used to set the location of the numeric boxes
on the page. 

## Grids of questions

You can also ask multiple horizontal or vertical questions using 
answers that share the same scale.

```{r}
# Vertical questions, horizontal answers
make_grid_question(
  question_prompt = "Rate the following items from 1 (not great) to 5 (not bad).",
  comment = "\\emph{Try to remain unenthused}",
  vertical_labels = c("Hi-Fives","Rollercoasters","Quiet Strolls"),
  horizontal_labels = 1:5,
  concat = T)
# Horizontal questions, vertical answers
make_grid_question(
  question_prompt = "Rate the following items from 1 (not great) to 5 (not bad).",
  comment = "\\emph{Try to remain unenthused}",
  vertical_labels = 1:5,
  horizontal_labels = c("Hi-Fives","Rollercoasters","Quiet Strolls"),
  concat = T)
```

## Prompts or arbitrary additions 

You can also add in any of the usual `.tex` elements, such as  
lines, page breaks, prompts, or section titles. Be sure to add in an extra
"\\" whenever you need to add a backslash.

```{r}
make_prompt(prompt = "\\clearpage",concat = T)
```

# Making Surveys 

## Non-Randomized Surveys

## Simple-Randomized Surveys

## Complete-Randomized Surveys

## Arbitrary Randomization Schemes

To be continued...




